---
title: "Modele Regression logistique Reg Pol"
output: html_document
---

## Explication des variables :

### political regime : 
It distinguishes between closed autocracies (score 0), electoral autocracies (score 1), electoral democracies (score 2), and liberal democracies (score 3). 
Cela ressemble à un "indice" de démocratie : https://ourworldindata.org/regimes-of-the-world-data


### Human Rights: 

The scores capture the extent to which citizens' physical integrity is protected from government killings, torture,
political imprisonments, extrajudicial executions, mass killings and disappearances. Higher scores mean fewer
such abuses. A score of 0 means an average score relative to all countries and years. A score of 2 is two standard deviations better than the mean across all countries and years.

Données actualisées depuis

### Economic freedom 0 à 10 (10 best)

The index measures the degree of economic freedom present in five major areas: [1] Size of Government; [2] Legal System and Security of Property Rights; [3] Sound Money; [4] Freedom to Trade Internationally; [5] Regulation. Within the five major areas, there are 42 distinct variables, which are averaged to derive the summary rating for each country. Scores are on a scale of 0-10, where 10 represents maximum economic freedom.

### Gender - inequality 0 à 1 (0 moins d'inégalités)

The GII is an inequality index. It shows the loss in potential human development due to disparity between female and male achievements in two dimensions, empowerment and economic status. The GII ranges between 0 and 1. Higher GII values indicate higher inequalities and thus higher loss to human development.
(critiqué par certains auteurs mais utilisé par les nations unies)

### Bullied % d'enfants 

Percentage of children aged 13-15 who reported being bullied at least once in the past couple of months.

### Corruption (100 (très propre) à 0 (très corrompu)

Annual ranking of countries by their perceived levels of corruption, as determined by expert assessments and opinion surveys. Scale is from 100 (very clean) to 0 (highly corrupt).

### Litteracy Rate % sachant lire et ecrire

Estimates correspond to the share of the population older than 14 years that is able to read and write.

### HDI

The Human Development Index (HDI) is a summary measure of key dimensions of human development: a long and healthy life, a good education, and having a decent standard of living.

### Mean Year of schooling 

Average total years of schooling for adult population

### Life expectancy

Life expectancy at birth is defined as the average number of years that a newborn could expect to live if he or she were to pass through life subject to the age-specific mortality rates of a given period.

### Millitary expdenditure (% PIB)

Military expenditure as a share of GPD

GPD = PIB (permet de quantifier la valeur totale de la « production de richesse » annuelle effectuée par les agents économiques (ménages, entreprises, administrations publiques) résidant à l'intérieur d'un territoire.)

problème avec ces données aussi. Elles ont été mises à jour.

### Undernourishment %

Share of people of the population who are undernourished
Undernourishment measures the share of the population that has a caloric intake which is insufficient to meet the
minimum energy requirements necessary for a given individual. 
Add region

### Internet %

Share of the population using the Internet

### Electricity %

the percentage of population with access to electricity

### Urban and rural population (nombre)

Number of individuals living in cities or not



```{r}
library(dplyr)
library(ggplot2)
library(corrplot)
library(readxl)
library(FactoMineR)
library(factoextra)
library(cowplot)
library("NbClust")
library(missForest)


library(MASS)
library(leaps)
library(bestglm)
library(ggfortify)
library(gridExtra)
```



```{r}
data3=read.csv("data3-modif.csv",header=TRUE,sep=";",dec=",")
rownames(data3)<-data3$Entity
data3=data3[,-1]
print(data3)
```

On supprime les pays dont nous n'avons pas l'indice Regime politique


```{r}
data3 =data3 %>% filter(!is.na(Regime_politique))
print(data3)
``` 



```{r}
#On fait un missing tree pour compléter les données manquantes et pas être embétés ensuite

data3=missForest(data3)$ximp #on fait un miss forest pour compléter les données manquantes et ne pas avoir de problèmes de NA dans la suite de l'analyse.
```





# Regression logistique partie 1
On va rassembler les pays dont le Regime politique est 0 et 1 et ceux dont l'indice est 2 et 3


closed autocracies (score 0), electoral autocracies (score 1), electoral democracies (score 2), and liberal democracies (score 3)
In closed autocracies, citizens do not have the right to either choose the chief executive of the government or the legislature through multi-party elections.

In electoral autocracies, citizens have the right to choose the chief executive and the legislature through multi-party elections; but they lack some freedoms, such as the freedoms of association or expression, that make the elections meaningful, free, and fair.

In electoral democracies, citizens have the right to participate in meaningful, free and fair, and multi-party elections.

In liberal democracies, citizens have further individual and minority rights, are equal before the law, and the actions of the executive are constrained by the legislative and the courts.

#Rassemblement 0 et 1 en 0 et 2 et 3 en 1 dans la variable Regime Pol 2
```{r}
data3$Regime_politique2 <- 0 # autocratie
data3$Regime_politique2[data3$Regime_politique == 2] <- 1
data3$Regime_politique2[data3$Regime_politique == 3] <- 1
head(data3)
``` 


```{r}
glm.Regime_pol2= glm(Regime_politique2 ~ .-Regime_politique, data=data3, family=binomial(link="logit"))
summary(glm.Regime_pol2)
```

le pseudo $R^2$ associé à ce modèle et commentez.

```{r}
pseudoR2 = (glm.Regime_pol2$null.deviance - glm.Regime_pol2$deviance)/glm.Regime_pol2$null.deviance
pseudoR2
```

pseudoR²=0.47 c'est moyen

Le modele constant est-il envisageable ?

```{r}
M0 = glm(Regime_politique2 ~ 1, data=data3, family=binomial(link="logit"))
summary(M0)
anova(M0,glm.Regime_pol2,test="Chisq")
```
Avec Anova : p-valeur <2.2e-16 <0.05 donc on rejette Ho c'est à dire que le modele constant n'est pas adapté.


```{r}
exp(glm.Regime_pol2$coefficients)
```
1.8=exp(teta1)ôbs=OR(x+1,x)
où x est une valeur de Droit de l'Homme, donc si la variable Droit de l'Homme augmente de 1 on a 1.8 fois plus de chance d'avoir du une democratie.



# Sélection de variables :
#Critère AIC
```{r}
step(glm.Regime_pol2,trace=TRUE,direction=c("backward"))

```
sous modele retenu :
Regime_politique2 ~ Droit_de_lHomme + Corruption + Budget_militaire_from_GPD + Sous_alimentation + Pop_urban + Pop_rural

```{r}
modselect_AIC = glm(Regime_politique2 ~ Droit_de_lHomme + Corruption + HDI + Budget_militaire_from_GPD + Sous_alimentation + Pop_urban + Pop_rural, data=data3, family = binomial(link="logit"))
```

```{r}
anova(modselect_AIC,glm.Regime_pol2,test="Chisq")
``` 
p-val =0.89 > 0.05 donc on accepte l'hypothese cad que le sous modele est accepté

#Critère BIC
```{r}
step(glm.Regime_pol2, trace=FALSE,direction="backward", k=log(nrow(data3)))

```

On garde les variables droit de l'Homme, corruption, budget militaire , pop rural et pop urban (même que AIC moins sous alimentation) pour exprimer le régime politique (2)

````{r}
modselect_BIC=glm(formula = Regime_politique2 ~ Droit_de_lHomme +Corruption +Budget_militaire_from_GPD+ Pop_rural +Pop_urban, family = binomial(link = "logit"),  data = data3)


anova(modselect_BIC,glm.Regime_pol2,test="Chisq")
```
pval=0.74 on accepte le sous modele

